---
title: "Rtinder: Unofficial API Tinder for R"
output: github_document
---

R client for accessing Tinder's API.

I could not find any scientific project for which to use Tinder data, **I would love to be informed about the idea that comes to you**.

Since the tinder API is not publicly open. Without the github repository
https://github.com/fbessez/Tinder , Rtinder would not have been possible.

## Features

* Provides an interface to the tinder API.

* Allows swiping, getting matches, sending messages, among other functions.

## Installation

Rtinder is only available as a GitHub package. To install it run the following
from an R console:

```{r eval=FALSE}
if (!require("remotes")) {
  install.packages("remotes")
}
remotes::install_github("jcrodriguez1989/Rtinder")
```

## Usage

From an R console type:

```{r}
library("Rtinder")
```
```{r eval=FALSE}
# When first using Rtinder, we should configure the account.
# It will save (by default) the config file in ~/.tinderAccount.R
# It will save just the access token, not the mail nor the password.
# Wont send info to any server besides Facebook.
# You can see configAccount, it is open source ;)
configAccount("MY_FB_REGISTERED_MAIL", "MY_FB_PASSWORD")

# or by SMS with
configAccountSms(MY_PHONE_NUM) # configAccountSms(543516881918)
```
```{r eval=TRUE}
# Now we can check if it can connect to tinder.
# login() must be executed each time we load Rtinder library.
invisible(login())
# And finally we can start swiping!
mySwipes <- getSwipes()
# mySwipes is a list
fstSwipe <- mySwipes[[1]]
# fstSwipe is a list
names(fstSwipe)
names(fstSwipe$user)
```
